Ownership types in theory and practice (in Rust)

### 2022-11-27 notes.tex
Added notes file

Object aliasing is the concept of accessing memory through different symbolic names in object-oriented programming languages.
Many progamming bugs are created through unintentional aliases, which are hard to detect and can lead to unexpected side-effects.
Ownership types are one solution that attempt to prevent many alias-related bugs.
There are different specific implementations of ownership types, but the premise is that 
The premise of ownership types is that not only the fields of an object are protected from external access, but also all (recursively defined) objects stored in those fields.
This is done by allowing objects to take ownership of other objects.
% TODO: add citation\cite{ownership-types-survey}

This paper introduces the different kinds of ownership types and explains how the modern programming language Rust uses ownership types to garantue memory safety.

@@

% QUESTIONS:
% - difference between aliases and references
% - difference between "a is owner of b" and "b is outside a"

>>>>

@@

% QUESTIONS:
% - difference between aliases and references
% - difference between "a is owner of b" and "b is outside a"
% - how to reference that a whole paragraph came from one source?
